The Name of the Title Is Hope

### 2024-11-26 paper/paper.tex
some progress

Next, AI models are extracted from various real life authors from Kaggle. They are finetuned to perform well on the original dataset. For one, a random forest model is finetuned by searching hyperparameters settings\cite{Ipbyrne2023}. For another, a logistic regression model is finetuned by performing principal component analysis\cite{Prashant1112023}.

AI models and both the original dataset and the synthetic datasets are fed to the fairness checker. Sensitive attributes are identified based on manual examination with common sense or by referring to \cite{pessach2022review}. Then, all applicable fairness measures are computed using the checker for both the original dataset and the rounds of synthetic datasets.

@@

@@

\subsection{One More Dataset}

@@

% \begin{table}
%   \caption{Frequency of Special Characters}
%   \label{tab:freq}
%   \begin{tabular}{ccl}
%     \toprule
%     Non-English or Math&Frequency&Comments\\
%     \midrule
%     \O & 1 in 1,000& For Swedish names\\
%     $\pi$ & 1 in 5& Common in math\\
%     \$ & 4 in 5 & Used in business\\
%     $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
%   \bottomrule
% \end{tabular}
% \end{table}

% \begin{table*}
%   \caption{Some Typical Commands}
%   \label{tab:commands}
%   \begin{tabular}{ccl}
%     \toprule
%     Command &A Number & Comments\\
%     \midrule
%     \texttt{{\char'134}author} & 100& Author \\
%     \texttt{{\char'134}table}& 300 & For tables\\
%     \texttt{{\char'134}table*}& 400& For wider tables\\
%     \bottomrule
%   \end{tabular}
% \end{table*}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{compas_mst}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{adult_mst}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

>>>>

Next, several AI models are extracted from various real life authors from Kaggle. They are finetuned to perform well on the original dataset. For one, a random forest model is finetuned by searching hyperparameters settings\cite{Ipbyrne2023}. For another, a logistic regression model is finetuned by performing principal component analysis\cite{Prashant1112023}.

Several AI models and both the original dataset and the rounds of synthetic datasets are fed to the fairness checker. Sensitive attributes are identified based on manual examination with common sense or by referring to \cite{pessach2022review}. Then, all applicable fairness measures are computed using the checker for both the original and the synthetic.

@@

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{adult_mst}
\caption{Markov random field for marginals of the adult dataset.}
\Description{Markov random field for marginals of the adult dataset.}
\end{figure}

\begin{table}[h]
\caption{Fairness measures experiment results.}
\label{tab:categories}
\begin{tabular}{p{0.3\linewidth}cccc}
\toprule
\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Ratio} \\
\midrule
Demographic Parity  & 0.172 & 0.104 & 0.067 & 1.651 \\
Accuracy Eqaulity   & 0.047 & 0.117 & 0.069 & 0.404 \\
Equalized Odds 1    & 0.057 & 0.079 & 0.021 & 0.723 \\
Equalized Odds 2    & 0.166 & 0.122 & 0.044 & 1.365 \\
Accuracy Equality 1 & 0.100 & 0.132 & 0.031 & 0.759 \\
Accuracy Equality 2 & 0.119 & 0.146 & 0.027 & 0.814 \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{compas_mst}
\caption{Markov random field for marginals of the COMPAS dataset.}
\Description{Markov random field for marginals of the COMPAS dataset.}
\end{figure}

\begin{table}[h]
\caption{Fairness measures experiment results.}
\label{tab:categories}
\begin{tabular}{p{0.3\linewidth}cccc}
\toprule
\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Ratio} \\
\midrule
Demographic Parity     & 0.131 & 0.098 & 0.032 & 1.329 \\
Accuracy Eqaulity      & 0.007 & 0.013 & 0.005 & 0.575 \\
Equalized Odds 1       & 0.024 & 0.099 & 0.074 & 0.249 \\
Equalized Odds 2       & 0.017 & 0.097 & 0.079 & 0.182 \\
Accuracy Equality 1 & 0.170 & 0.082 & 0.088 & 2.082 \\
Accuracy Equality 2 & 0.169 & 0.027 & 0.141 & 6.058 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Diabetes Dataset}

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{diabetes_mst}
\caption{Markov random field for marginals of the diabetes dataset.}
\Description{Markov random field for marginals of the COMPAS dataset.}
\end{figure}

\begin{table}[h]
\caption{Fairness measures experiment results.}
\label{tab:categories}
\begin{tabular}{p{0.3\linewidth}cccc}
\toprule
\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Ratio} \\
\midrule
Demographic Parity  & 0.013 & 0.015 & 0.002 & 0.867 \\
Accuracy Eqaulity   & 0.007 & 0.009 & 0.002 & 0.782 \\
Equalized Odds 1    & 0.000 & 0.003 & 0.003 & 0.000 \\
Equalized Odds 2    & 0.008 & 0.106 & 0.097 & 0.081 \\
Accuracy Equality 1 & 0.013 & 0.097 & 0.084 & 0.136 \\
Accuracy Equality 2 & 0.021 & 0.020 & 0.001 & 1.068 \\
\bottomrule
\end{tabular}
\end{table}

@@
